The helicoverpa package

### 2018-07-23 notebook/helicoverpa_notes.Rmd
Attempt to add a comment section

     - **JUL** [18](#u-18-JUL-2018),

@@

@@

References

>>>>

     - **JUL** [18](#u-18-JUL-2018), **JUL** [23](#u-23-JUL-2018)

[Project comments](#comments)

@@

> <a name="u-23-JUL-2018">Update: 23 JUL 2018</a>

I have attempted to set this notebook up with [Disqus](https://disqus.com/) commenting enabled with [the universal code optoins](https://helicoverpa.disqus.com/admin/install/platforms/universalcode/) (embedded HTML), which will ideally allow everyone on the project to make comments on the notes.

Data structures
--------------------------------------------------------------------------------

There are two data structures that we need to think about in particular, and these include the **pests**, which will be represented individually

@@

Comments {.comments}
--------------------------------------------------------------------------------

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL; https://bradduthie.github.io/helicoverpa/notebook/helicoverpa_notes.html
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://helicoverpa.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>

References
--------------------------------------------------------------------------------
